\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,enumitem,clrscode3e}
\usepackage[margin=1in]{geometry}

\title{\bf Assignment 6 \\[2ex]
\rm\normalsize Due: March 3, 2020}
\date{}
\author{
  Kanyid, Bradon\\
  \texttt{bradon.kanyid@pdx.edu}
  \and
  Reimer, Daniel\\
  \texttt{daniel.reimer@pdx.edu}
}
\begin{document}
\maketitle

\begin{center}
    \fbox{\fbox{\parbox{\textwidth}{\centering
    Your solutions must be typed (preferably typeset in \LaTeX ) and submitted as a hard-copy at the beginning of
    class on the day its due.
    \\

    When asked to provide an algorithm you need to give well formatted pseudocode, a description of how your
    code solves the problem, and a brief argument of its correctness.
    }}}
\end{center}

\paragraph{Problem 1: Longest-Probe Bound for Hashing}
Suppose we use an open-addressed hash table (section 11.4 in CLRS) of size $m$ to store $n \leq \frac m2$ items.

\subparagraph{(a) [10 points]}
Assuming simple uniform hashing, show that for $i = 1,2,...,n$, the probability is at most $2^{-k}$ that the $i$th
insertion requires strictly more than $k$ probes.

\input{solutions/sol1a}

\subparagraph{(b) [10 points]}
Assuming simple uniform hashing, show that for $i = 1,2,...,n$, the probability is $O(\frac 1{n^2})$ that the
$i$th insertion requires more than $2 \lg n$ probes.

\input{solutions/sol1b}

\paragraph{Problem 2: Building a Queue using Stacks}
It is possible to build a {\em queue} (FIFO) using two stacks. Assume that the stacks have three operations, {\em push}, {\em pop}, and {\em isEmpty}, each with cost 1. A queue can be implemented as follows:
\begin{itemize}
\item {\em enqueue:} push item $x$ onto stack 1
\item {\em dequeue:} if stack 2 is empty then pop the entire contents of stack 1 pushing each element in turn onto stack 2. Now pop from stack 2 and return the result.
\end{itemize}
A conventional worst-case analysis would establish that {\em dequeue} takes $O(n)$ time, but this is clearly a weak bound for a sequence of operations, because very few dequeues will actually take that long. To simplify your analysis only consider the cost of the push and pop operations.

\subparagraph{(a) [10 points]}
Using the aggregate method show that the amortized cost of each {\em enqueue} and {\em dequeue} is constant.

\input{solutions/sol2a}

\subparagraph{(b) [10 points]}
Using the accounting method show that the amortized cost of each {\em enqueue} and {\em dequeue} is constant.

\input{solutions/sol2b}

\subparagraph{(c) [10 points]}
Using the potential method show that the amortized cost of each {\em enqueue} and {\em dequeue} is constant.

\input{solutions/sol2c}

\end{document}
