\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,enumitem}
\usepackage[margin=1in]{geometry}

\title{\bf Assignment 1 \\[2ex]
\rm\normalsize Due: January 16, 2020}
\date{}
\author{}

\begin{document}
\maketitle

\begin{center}
    \fbox{\fbox{\parbox{5.5in}{\centering
        Your solutions must be typed (preferably typeset in \LaTeX ) and submitted as a hard-copy at the beginning of
        class on the day its due.
        \\

        When asked to provide an algorithm you need to give well formatted pseudocode, a description of how your
        code solves the problem, and a brief argument of its correctness.
    }}}
\end{center}

\paragraph{Problem 1: Asymptotic Analysis Practice}
\subparagraph{(a) [5 points]}
Prove or disprove that $\log_k n \in O(\lg n)$ for any $k > 1$. (Note that $\lg$ refers to $\log_2$)
\subparagraph{(b) [5 points]}
The following recurrence relation solves to $O(n \lg^2 n)$. Prove this by substition. Do not use the Master method.
\begin{align*}
T(n) &= 2T\left( \frac n2 \right) + n \lg n \\
T(1) &= 0
\end{align*}
\subparagraph{(c) [5 points]}
Suppose that $f(n)$ and $g(n)$ are non-negative functions. Prove or disprove the following: if $f(n) \in O(g(n))$ then $2^{f(n)} \in O(2^{g(n)})$.


\paragraph{Problem 2: Peak-finding}
Given a set of real numbers stored in an array $A$ find the index of a {\em Peak}, where a {\em Peak} is defined as an
element that is larger or equal to the both the elements on its sides. (Note: you only need to return {\em a} peak, not
the highest one.)\\

Example array:
                {\tt
                \begin{tabular}{|*{9}{r|}}
                    \hline
                    -2 & \ 6 & -1 & \ 4 & \ 9 & -5 & \ 5  \\
                    \hline
                \end{tabular}
                }

Assuming the array one based it has peaks at indices $\{2,5,7 \}$.

\subparagraph{(a) [5 points]}
Give a linear time algorithm to solve this problem. (This should be obvious)
\subparagraph{(b) [10 points]}
Give a $O(\log n)$ time algorithm to solve this problem.
\subparagraph{(c) [10 points]}
What if instead of a simple array you are given a square matrix, where a {\em Peak} is now defined as an element larger
or equal to its four neighbours. Give a $O(n \log n)$ solution to this variant of the problem.

\end{document}
