\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,enumitem,clrscode3e}
\usepackage[margin=1in]{geometry}

\title{\bf Assignment 2 \\[2ex]
\rm\normalsize Due: January 23, 2020}
\date{}
\author{
  Kanyid, Bradon\\
  \texttt{bradon.kanyid@pdx.edu}
  \and
  Reimer, Daniel\\
  \texttt{daniel.reimer@pdx.edu}
}
\begin{document}
\maketitle

\paragraph{Problem 1: Jarvis March (Gift Wrapping Algorithm)}
For this question you will need to research the {\em Jarvis March} convex hull algorithm. Be sure to cite your sources (ACM or IEEE formatted is preferred).
\subparagraph{(a) [10 points]}
Give pseudocode describing the Jarvis March algorithm, a brief description of how it works, and explain its best and worst case efficiency.
\input{solutions/hw1a}
\subparagraph{(b) [5] points}
Give an example input on which Jarvis March will perform significantly better than Graham's scan and explain why it will perform better.
\input{solutions/hw1b}
\subparagraph{(c) [5] points}
Give an example input on which Graham's Scan will perform significantly better than Jarvis March and explain why it will perform better.
\input{solutions/hw1c}

\paragraph{Problem 2: Find the Missing Number}
You are given a list of $n-1$ integers $A$, in the range of 1 to $n$. There are no duplicates in the list. One of the integers is missing.
(Feel free to assume that $n = 2^m$ for some integer $m$)
\subparagraph{(a) [5 points]}
Give an efficient algorithm for finding the missing number, show its complexity, and argue its correctness.
(You should try for $O(n)$-time and $O(1)$-space, less efficient solutions will still get partial credit)
\input{solutions/hw2a}
\subparagraph{(b) [10 points]}
For this question you are not allowed to access an entire integer with a single operation. The elements of the list are represented in binary, and the only operation you can use to access them is \proc{GetBinaryDigit(A[i],j)} which returns the $j$th bit of element $A[i]$ which runs in constant time. Give an efficient algorithm for finding the missing number under these constraints, show its complexity, and argue its correctness.
(You should try for $O(n)$-time and $O(log n)$-space, less efficient solutions will still get partial credit)

Example: If we run \proc{GetBinaryDigit($A[i]$,$j$)} with $A[i]=29$ and $j=2$, it would return a $0$ since $29=11101$.
\input{solutions/hw2b}

\end{document}
