\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,enumitem,clrscode3e}
\usepackage[margin=1in]{geometry}

\title{\bf Assignment 5 \\[2ex]
\rm\normalsize Due: February 25, 2019}
\date{}
\author{
  Kanyid, Bradon\\
  \texttt{bradon.kanyid@pdx.edu}
  \and
  Reimer, Daniel\\
  \texttt{daniel.reimer@pdx.edu}
}
\begin{document}
\maketitle

\begin{center}
    \fbox{\fbox{\parbox{\textwidth}{\centering
    Your solutions must be typed (preferably typeset in \LaTeX ) and submitted as a hard-copy at the beginning of
    class on the day its due.
    \\

    When asked to provide an algorithm you need to give well formatted pseudocode, a description of how your
    code solves the problem, and a brief argument of its correctness.
    }}}
\end{center}

\paragraph{Problem 1: Highway Safety [10 points]}
As is well-known, America’s highway infrastructure is crumbling. Yet travel must continue.
Suppose you are given a map of U.S. cities and roads connecting them that shows, for every road
segment, the probability of traveling down that segment {\em safely}, i.e. without destroying your axle
in a pothole, falling into a river due to a broken bridge, etc. Design and analyze an algorithm to
determine the safest route from Portland to your preferred summer vacation spot.

\paragraph{}
Stated more formally, suppose you are given a directed graph $G = (V,E)$, where every edge $e$ has an independent
safety probability $p(e)$. The safety of a path is the product of the safety probabilities
of its edges. Design and analyze an algorithm to determine the safest path from a given start vertex
$s$ to a given target vertex $t$.

\input{solutions/hw1}

\paragraph{Problem 2: MST}
The {\em cut property} makes it possible to build minimum
spanning trees greedily, starting from an empty graph and adding one edge at a time. A different approach
is to start with the original graph and remove edges greedily, one at a time, until an MST remains. A
scheme of this second type can be justified by the following property.
\begin{quote}
Pick any cycle in the graph, and let $e$ be the heaviest edge in that cycle. Then there is a
minimum spanning tree that does not contain $e$.
\end{quote}
\subparagraph{(a) [5 points]}
Prove this {\em cycle property}.

\input{solutions/hw2a}

\subparagraph{(b) [5 points]}
Use the property to justify the following MST algorithm. The input is an undirected graph
$G = (V, E)$ with edge weights $\{ w_e \}$.

\begin{codebox}
\li sort the edges according to their weights
\li \For each edge $e \in E$, in decreasing order of $w_e$
    \Then
    \li \If $e$ is part of a cycle of $G$
        \Then
        \li $G = G - e$ (that is, remove $e$ from $G$)
        \End
    \End
\li \Return G
\end{codebox}

\input{solutions/hw2b}

\subparagraph{(c) [5 points]}
On each iteration, the algorithm must check whether there is a cycle containing a specific edge $e$.
Give a linear-time algorithm for this task, and justify its correctness.

\input{solutions/hw2c}

\subparagraph{(d) [5 points]}
What is the overall time complexity of this algorithm, in terms of $|E|$? Explain your answer.

\input{solutions/hw2d}

\end{document}
